Fractional Decomposition Trees: A tool for studying mixed-integer-program integrality gaps

### 2018-11-21 IPCO format/introduction.tex
compress

More generally we can define the integrality gap for a class of instances $\mathcal{I}$:% In this case, the integrality gap for problem $\mathcal{I}$ is
\begin{equation}
g_\mathcal{I} = \max_{c\geq 0 , I\in\mathcal{I}}\frac{z_{IP}(I,c)}{z_{LP}(I,c)}
\end{equation}
For example, finding a  minimum-weight 2-edge-connected multigraph has a natural formulation: constraining every cut to be crossed at least twice.  The gap for this formulation is at most $\frac{3}{2}$ \cite{Wolsey1980} and at least $\frac{6}{5}$ \cite{carr-ravi}. Therefore, we cannot hope to obtain an LP-based $(\frac{6}{5}-\epsilon)$-approximation algorithm for this problem using this LP relaxation.

@@

\paragraph{Decomposition} Our methods will take advantage of theory connecting integrality gaps to sets of feasible solutions. Instances $I$ with  $g_I=1$ has $P(I)=\conv(S(I))$ where $\conv(S(I))$ is the convex hull of the lattice of feasible points. In this case, $P(I)$ is an \textit{integral} polyhedron. The spanning-tree polytope and the perfect-matching polytope \cite{schrijver} have this property. For such problems there is an algorithm to express vector $x\in P(I)$ as a convex combination of points in $S(I)$ in polynomial time \cite{cons-cara}.
\begin{proposition}\label{cara}
	If $g_I=1$, then for $(x,y)\in P(I)$, there exists $\theta \in [0,1]^k$, where $\sum_{i=1}^{k}\theta_i =1$ and $(\tilde{x}^i,\tilde{y}^i)\in S(I)$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k}\theta_i \tilde{x}^i\leq x$. Moreover, we can find such a convex combination in polynomial time.
\end{proposition}

>>>>

More generally we can define the integrality gap for a class of instances $\mathcal{I}$:% In this case, the integrality gap for problem $\mathcal{I}$ is
\begin{equation}
g_\mathcal{I} = \max_{c\geq 0 , I\in\mathcal{I}}\frac{z_{IP}(I,c)}{z_{LP}(I,c)}
\end{equation}
For example, finding a  minimum-weight 2-edge-connected multigraph has a natural formulation: every cut is crossed at least twice.  The gap for this formulation is at most $\frac{3}{2}$ \cite{Wolsey1980} and at least $\frac{6}{5}$ \cite{carr-ravi}. Therefore, we cannot hope to obtain an LP-based $(\frac{6}{5}-\epsilon)$-approximation algorithm for this problem using this LP relaxation.

@@

\paragraph{Decomposition} Our methods apply theory connecting integrality gaps to sets of feasible solutions. Instances $I$ with  $g_I=1$ has $P(I)=\conv(S(I))$, the convex hull of the lattice of feasible points. In this case, $P(I)$ is an \textit{integral} polyhedron. The spanning-tree polytope and the perfect-matching polytope \cite{schrijver} have this property. For such problems there is an algorithm to express vector $x\in P(I)$ as a convex combination of points in $S(I)$ in polynomial time \cite{cons-cara}.
\begin{proposition}\label{cara}
	If $g_I=1$, then for $(x,y)\in P(I)$, there exists $\theta \in [0,1]^k$, where $\sum_{i=1}^{k}\theta_i =1$ and $(\tilde{x}^i,\tilde{y}^i)\in S(I)$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k}\theta_i \tilde{x}^i\leq x$. Moreover, we can find such a convex combination in polynomial time.
\end{proposition}
